EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-07-13 03_edipack2.tex

From a computational perspective, constructing a symmetry
sector amounts to defining an injective map
$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the consecutives indexing of the electronic states  $\ket{i}$
within a given symmetry sector $\SS_{\vec{Q}}$ to the Fock states $\ket{I_e}$ in the electronic Fock space in their number representation. 
This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
The global Fock state $\ket{I}=\ket{I_e}\ket{p}$, including the phonon part, is univocally determined by the relation: $I\to I_e + p\,2^{2 N_s}$.

@@

\paragraph{{\bf superc}.}
In the superconductive case, the orbital-dependent Nambu $s$-wave
Green's function has the form:
\begin{equation}
  \label{GFnambu}
  \hat{G}_{\a\b} =
  \begin{bmatrix}
    G_{\a\b\up\up} & F_{\a\b\up\dw} \\
    \bar{F}_{\a\b\dw\up} & \bar{G}_{\a\b\dw\dw}.
  \end{bmatrix}  
\end{equation}
Exploiting symmetries between matrix components, it is 
sufficient to compute only the top row elements along with 
a few auxiliary functions \cite{Capone2001PRL,Capone2002Science,Capone2004PRLsc,Toschi2005NJP,Toschi2005PRB,Capone2009RMP}.
%
The diagonal, normal, component $G_{\a\a\up\up}$ can be 
evaluated using the same approach as in the {\tt ed\_mode=}{\bf normal} 
case. However, for the off-diagonal terms $G_{\a\b\up\up}$, 
we forgo symmetry arguments and instead define two 
auxiliary operators, $\OO = c_{\a\up} + c_{\b\up}$ and 
$\PP = c_{\a\up} - i c_{\b\up}$. This allows us to express 
the Green's function as
$G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
(1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})$.

>>>>

From a computational perspective, constructing a symmetry
sector amounts to defining an injective map
$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the consecutive indexing of the electronic states  $\ket{i}$
within a given symmetry sector $\SS_{\vec{Q}}$ to the Fock states $\ket{I_e}$ in the electronic Fock space in their number representation. 
This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
The global Fock state $\ket{I}=\ket{I_e}\ket{p}$, including the phonon part, is univocally determined by the relation: $I\to I_e + p\,2^{2 N_s}$.

@@

\paragraph{{\bf superc}.}
In the superconductive case, the orbital-dependent Nambu $s$-wave
Green's function has the form:
\begin{equation}
  \label{GFnambu}
  \hat{G}_{\a\b} =
  \begin{bmatrix}
    G_{\a\b\up\up} & F_{\a\b\up\dw} \\
    \bar{F}_{\a\b\dw\up} & \bar{G}_{\a\b\dw\dw}.
  \end{bmatrix}  
\end{equation}
Exploiting symmetries between matrix components, it is 
sufficient to compute only the top row elements along with 
a few auxiliary functions \cite{Capone2001PRL,Capone2002Science,Capone2004PRLsc,Toschi2005NJP,Toschi2005PRB,Capone2009RMP}.
%
The diagonal, normal, component $G_{\a\a\up\up}$ can be 
evaluated using the same approach as in the {\tt ed\_mode=}{\bf normal} 
case. However, for the off-diagonal terms $G_{\a\b\up\up}$, 
we forgo symmetry arguments and instead define two 
auxiliary operators, $\OO = c_{\a\up} + c_{\b\up}$ and 
$\PP = c_{\a\up} - i c_{\b\up}$. This allows us to express 
the Green's function as
$G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
(1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})]$.
